### 2016-03-14 paper/optical_flow.tex
yasu

Fusion Move was first introduced by Lempitsky et al.~\cite{fusion_flow} to
solve the optical flow problem.
% Optical flow was the problem, in which the Fusion Move method was first
%introduced by Lempitsky et al.~\cite{viktor}.
We copy their problem setting and use images from the Middlebury optical flow
benchmark~\cite{middlebury_optical_flow}. We share similar proposal generation schemes with Lempitsky et al~\cite{fusion_flow}, but instead of the HS algorithm, we use more recent Farneback algorithm and change its pyramid levels from 1 to 5 and use either 3, 5 or 7 for parameter polyN. Besides the clustering idea, we add three simple proposal generation schemes based on the current solution as suggested in ~\cite{fusion_flow}. In \textit{shift proposal}, the flow field in the current solution is shifted in either x direction or y direction for either 1, 2 or 3 pixels. In \textit{stagger proposal}, the flow field is shifted by a vector randomly drawed from a Gaussian distribution. In \textit{disturb proposal}, each flow value in the field is indenpendantly shifted by a vector randomly drawed from a Gaussian distribution. We choose schemes randomly when generating proposals.

>>>>

Fusion Move was first introduced by Lempitsky et al.~\cite{fusion_flow} to
solve the optical flow problem.
% Optical flow was the problem, in which the Fusion Move method was first
%introduced by Lempitsky et al.~\cite{viktor}.
We copy their problem setting and use images from the Middlebury optical
flow benchmark~\cite{middlebury_optical_flow}. We share similar proposal
generation schemes with Lempitsky et al~\cite{fusion_flow}, but
%instead of the HS algorithm, we
use more recent Farneback algorithm with some modifications.~\footnote{First, we
change the level of pyramids from 1 to 5, then use either 3, 5 or 7 for
parameter ``polyN''. Besides the clustering idea, we add three simple
proposal generation schemes based on the current solution as suggested
in \cite{fusion_flow}. In \textit{shift proposal}, the flow field in the
current solution is shifted in either x or y directions for
either 1, 2 or 3 pixels. In \textit{stagger proposal}, the flow field is
shifted by a vector randomly drawn from a Gaussian distribution. In
\textit{disturb proposal}, each flow value in the field is
indenpendantly shifted by a vector randomly drawn from a Gaussian
distribution. We choose schemes randomly when generating proposals.}

### 2016-03-14 paper/stereo.tex
yasu

\section{Swarm Fusion instantiation}
\hang{I didn't understand the organization of this section at the
  first glance. Should it be clearer if we put 'Swarm fusion
  architectures' in front of 'Competing methods' in each problem?}

@@

\subsection{Swarm Fusion stereo}
We start with a simple depthmap stereo problem with standard unary and
pairwise terms. We employ submodular pairwise terms to make this
stereo represent relatively ``easy'' MRF inference problems.
%
Unary terms are computed as the average robust photoconsistancy
score~\cite{second_order_stereo} between the reference image and the others
inside a $7\times 7$ pixels window.  Pairwise terms are simple
truncated absolute label difference with maximum label difference
$\sigma_s=4$. The total energy is defined by the sum of the two, while
scaling the pairwise term by a factor of $0.005$. For simplicity we
don't enforce visibility constraint.

@@

\noindent The sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms dominant in most
stereo problems.  Our experiments have also supported this, where the
fusion method (i.e., the use of proposal generation) rather makes it
slow due to the overhead.\hang{Don't quite understand this
  sentence. Does the ``dominant'' means running time or energy? In my
  experiments, unary terms are pre-computed and are not counted into
  the running time} Therefore, we have chosen single thread Alpha
Expansion(AE), Parallel Alpha
Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
and Hierarchical
Fusion~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion}
with graph-cuts optimization as the competing methods.

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-SS (SF without solution sharing), SF-MF (SF without
multi-way fusion), and the standard SF.
%
SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set
to 4. In this case one thread will fuse 4 labels by TRW-S per
iteration and never exchanges solutions with other threads. SF-MF
implies $\alpha+\beta=1$, where each thread will expand 3 labels
(repeat $\alpha=1, \beta=0$ for 3 iterations) and then fuse one
solution from other threads ($\alpha=0, \beta=1$) by QPBO. In the later
case, a thread randomly chooses one target thread to grab solution
from. For standard SF, we have used ($\alpha=4, \beta=1$). For the
SF-SS architecture, we performed a final fuse of solutions from all
thread by multiway fusion.

%
%
%
%
To make the comparison simple, we restrict our proposal generator
in each thread to only generate constant-label proposals within a
subset of all labels. Graph-cuts is used in fusing a constant-label
proposal as the energy is submodular. QPBO is used in fusing a
different solution from another thread as the energy is typically
non-submodular.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.

>>>>

\section{Swarm Fusion instantiation}
% \hang{I didn't understand the organization of this section at the
%   first glance. Should it be clearer if we put 'Swarm fusion
%   architectures' in front of 'Competing methods' in each problem?}

@@

\subsection{Swarm Fusion stereo}
We start with a simple depthmap stereo problem with standard unary and
pairwise terms. We employ submodular pairwise terms to make this
stereo represent relatively ``easy'' MRF inference problems.
%
Unary terms are computed as the average robust photoconsistancy
score~\cite{second_order_stereo} between the reference image and the others
inside a $7\times 7$ pixels window.  Pairwise terms are simple
truncated absolute label difference with maximum label difference
$\sigma_s=4$. The total energy is defined by the sum of the two, while
scaling the pairwise term by a factor of $0.005$. For simplicity we
do not enforce the visibility constraint.

@@

\noindent The sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms highly informative
in most stereo problems.  Our experiments have also supported this,
where the fusion method (i.e., the use of proposal generation) rather
makes it slow due to the overhead.
%\hang{Don't quite understand this sentence. Does the ``dominant'' means
%running time or energy? In my experiments, unary terms are pre-computed
%and are not counted into the running time}
Therefore, we have chosen single thread Alpha Expansion(AE), Parallel
Alpha
Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
and Hierarchical
Fusion~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion}
with graph-cuts optimization as the competing methods.

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-SS (SF without solution sharing), SF-MF (SF without
multi-way fusion), and the standard SF.
%
SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set to
4. In this case one thread will fuse 4 labels by TRW-S per iteration and
never exchanges solutions with other threads. SF-MF implies
$\alpha+\beta=1$, where each thread will expand 3 labels (repeat
$\alpha=1, \beta=0$ for 3 iterations) and then fuse one solution from
other threads ($\alpha=0, \beta=1$) by QPBO. In the later case, a thread
randomly chooses one target thread to copy a solution. For standard SF,
we have used ($\alpha=4, \beta=1$). For the SF-SS architecture, we
perform a multi-way fusion at the end to fuse solutions from all the threads.

%
%
%
%
To make the comparison simple, we restrict our proposal generator
in each thread to only generate constant-label proposals within a
subset of all labels. Graph-cuts is used in fusing a constant-label
proposal as the energy is submodular. QPBO is used in fusing a
different solution from another thread as the energy is
non-submodular in general.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.
